This question involves the use of linear regression on the `Auto` data set from the textbook library `ISLR`. You could do `?Auto` to check the description of the dataset.

```{r}
library(tidyverse)
library(ISLR)
head(Auto)
```


(a) Use the `lm()` function to perform a linear regression with `mpg` as the response and `horsepower` as the predictor.

```{r}
model <- lm(formula = mpg ~ horsepower, data = Auto)
model
```

(b) Plot the response and the predictor as well as the regression line. Any comment?

A scatterplot of the data
```{r}
ggplot(Auto, aes(x = horsepower, y = mpg, color = horsepower)) + geom_point()
```

If we include the regression line of our model, we can see the fit.
```{r}
ggplot(Auto, aes(x = horsepower, y = mpg)) + geom_point() + geom_abline(slope = model$coefficients[2], intercept = model$coefficients[1])
```



(c) What's the prediction of `mpg` if `horsepower` is 100?

```{r}
predict.lm(model, new = data.frame(horsepower = 100))
```

The predicted miles per gallon is `24.15139`.

(d) What's the value of `R^2`? 

```{r}
summary(model)
```

The value of `R^2` in the model is `0.6059`.

### Model transformations

(e) Try a few different transformations of the predictor. And which is the best one you could find?

#### `log`

A good first transformation might be to look at the `log` of the dependent variable.
```{r}
model_log <-  lm(data = Auto, formula = mpg ~ I(log(horsepower)))
summary(model_log)
```

And a plot of the new model:
```{r}
ggplot(Auto, aes(x = log(horsepower), y = mpg)) + geom_point() + geom_abline(slope = model_log$coefficients[2], intercept = model_log$coefficients[1])
```

The value of `R^2` in the new model is `0.6892`, which is higher than in the original untransformed model. The plot shows that the line of fit is at least somewhat closer to the data 
in the extremes of the data set. The transformation seems to have somewhat improved our model.

#### `reciprocal`

.
```{r}
model_inv <-  lm(data = Auto, formula = I(1/mpg) ~ horsepower)
summary(model_inv)
```

And a plot of this model:
```{r}
ggplot(Auto, aes(x = horsepower, y = 1/mpg)) + geom_point() + geom_abline(slope = model_inv$coefficients[2], intercept = model_inv$coefficients[1])
```

With an `R^2` value of `.7307` this may may be a better fit than the other models considered.
Since the dataset contains multiple variables, but we are only considereing one independent
variable in the model, it may be that this variation represents the best possible fit we can find
for the data when only considereng one of the variables.


